What Makes New Coders Spend More Money

### 2021-04-26 outputs/paper/paper.Rmd
Edit text in paper.Rmd

---
title: "The Impact of Educational Expenses of New Coders"
subtitle: "The Factors Affecting Education Costs of Beginner Programmers to Learn to Code aside from University Tuition"
author: "Bongju Yoo"
thanks: "https://github.com/bonjwow/new-coders"
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: ""
output:
  bookdown::pdf_document2:
toc: FALSE
bibliography: references.bib
---

@@

Firstly, I processed correlation analysis to identify the relationship between each independent variable and dependent variable (education costs) pair and found that all the pairs have a positive linear relationship except for commuting time. Secondly, I used multiple linear regression to determine the statistical significance of the factors. The result of the analysis shows that commuting time is not statistically significant. Interestingly, education background is also not statistically significant associated with educational expenses of beginner programmers. Other variables, such as the size of city, income, and learning time, have a statistical significance on the costs.

This analysis shows that beginner programmers living in small towns and/or low-income households are likely to spend less money on learning to code aside from university tuition than those who live in bigger cities and/or high-income households. It is assumed that there is still a lack of educational resources for new coders living in rural areas and/or low-income households. Free online learning platforms such as freeCodeCamp can be a great resource of education for the coders.

>>>>

---
title: "What Makes New Coders Spend More Money"
subtitle: "The Factors Affecting Beginner Programmers' Expenses to Learn to Code"
author: "Bongju Yoo"
thanks: "Code and data are available at: [https://github.com/bonjwow/new-coders]"
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "I examine potential factors that may affect education costs of new coders to learn to code aside from their post secondary education based on the responses of the online survey run by freeCodeCamp in 2017. I use a correlation matrix and linear regression models to see if there is a correlation and causal relationship between the potential factors and the costs of learning to code. The results of the analysis show that a commuting time to work and the level of education do not affect educational expenditure of new coders to learn to code. It is also found that there is a correlation between each of the independent variables and the dependent variable, excluding a commuting time; however, there is no significant causal relationship between the variables. \\par \\textbf{Keywords:} Programmers, Coder, Education Costs, Coding, Online education, Open education"
output:
  bookdown::pdf_document2:
toc: FALSE
bibliography: references.bib
---

@@

Firstly, I processed correlation analysis to identify the relationship between each independent variable and dependent variable (the costs of learning to code) pair and found that all the pairs have a positive linear relationship except for a commuting time. Secondly, I used a combination of simple linear regression models and multiple linear regressions to determine the statistical significance of the factors. The result of the analysis shows that the level of education is not statistically significant on the new coders’ expenses to learn to code. Also, the analysis shows that the income of the programmers is statistically significant on the costs. So, it can be argued that those beginner programmers living in small towns and/or low-income households are likely to spend less money on learning to code aside from college or university tuition than those who live in bigger cities and/or high-income households. It is assumed that there is still a lack of educational resources for new coders living in rural areas and/or low-income households. Free online learning platforms such as freeCodeCamp can be a great resource of education for the coders. Unfortunately, all the regression models used to examine the effect of new coders' income had an extremely low R-squared score. So, it fails to compute the average of predicted costs of the programmers with specific values of the independent variable(s).
